Thesis Draft

### 2015-10-11 chapter2.tex
project
Former-commit-id: 6a321ecceabb2742ad2afb8404c3666df379d103

% HERE Same sample phrases are listed you can use them:

@@

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% HERE Same sample phrases are listed you can use them:

% The work that follows is divided into three sections

@@

% this thesis takes a rather different approach to the resonant possibilities of discarded things. It looks to philosophical ideas and our entangled experiences of things, time and stories, which need to be traversed in order for a discarded object to be called ‘waste’.

% I also want to suggest a different way of considering trash. Maybe art maybe suggest an alternative way of seeing.

% I’d like to criticise a set of concepts or ways of thinking about discarded things that to me just don’t seem quite adequate.

@@

% FROM Waste by William Viney
Douglas argues that our classification of dirt lies not with what objects are but where those objects are. (Think that the transformation process. Previous argument support that the transformation of trash is possible by changing the place of them. In other words removing them from landfill and waste bins to the book selves accomplish to transform trash.) ‘Dirt’, writes Douglas, ‘is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements’. For Douglas dirt is a spatial problem, a question of not what stuff is but where it is.

% “Dirt”, writes Douglas, “is the by-product of a systematic ordering and classification of matter, in so far as ordering involves rejecting inappropriate elements.” Dirt is only dirty in certain places, when it is out of its correct position. Just as faeces, for example, is considered dirty when it is in our kitchens but not when it is in our bodies, so it is that our classification of waste depends on the location of objects.

%%% My experience here: For example when i collect the papers under the dishes or food packages, people often thinks that it is disgusting and call them as dirty. But it is very strange that the fat on the paper is previously what they are eat.

% objects we call ‘waste’ have peculiar powers to make that temporality an explicit part of what they are and how we judge them.

% Here susan strasser ile douglasın fikirlerinde bir ortak nokta görülebilmekte. Özellikle trashın relative olması ve bu işin aslında bir ordering and classification olduğu konusunda. Remember the example given: shoes  on the dinner table.

% King Lear, feeling of waste

% waste is “matter is out place”, a definition first given by Lord Palmerston in the mid-nineteenth century and incubated by the British anthropologist Mary Douglas, in her book Purity and Danger.

% I prefer to use the word waste to describe the things that have, for whatever reason, been leftover from use or for which use has been precluded.

% https://narratingwaste.wordpress.com/tag/king-lear/
% Not all waste is dirty, it not always dangerous, contagious or abject. \ldots waste might be quite useful in making time and in keeping time.

% Binding things together and separating things from each other.

% Cornelia Parker's work, narrate an absent event of waste
% There is also strong relationship with the collecting discarded stuff and archeologies of waste.

### 2015-10-11 chapter3.tex
project
Former-commit-id: 6a321ecceabb2742ad2afb8404c3666df379d103

Artifact exploration promotes historical thinking, literacy investigation, and cultural expression (Higgs & McNeal, 2006; Levstik \& Barton, 2001; Morris, 1998). Meanings are embedded within cultural artifacts and language (Vygotsky, 1978).

>>>>

Artifact exploration promotes historical thinking, literacy investigation, and cultural expression (Higgs \& McNeal, 2006; Levstik \& Barton, 2001; Morris, 1998). Meanings are embedded within cultural artifacts and language (Vygotsky, 1978).

### 2015-10-11 chapter4.tex
project
Former-commit-id: 6a321ecceabb2742ad2afb8404c3666df379d103

\chapter{My work}
In this chapter the artwork explained in detail.

@@

%%
%%
\subsection{(Overcomed) Problems}
There are a lot of questions and problems that I have to overcome while development of my work. 
\begin{itemize}
\item First one is that my art work can be considered as design and has functional purposes. (It is not just a design, it is uses design to reach its goal like many artworks use other disciplines to reach their goals and expression. Purpose is not design and functionality.)
\item Using unused industrial paper. (Mixed trash and virgin material, \textbf{to show that discarded and desired object can live together.})
\item Collecting them.
\item Giving them to people, but people should take them voluntarily.
\end{itemize}

@@

>>>>

\chapter{My work}
In this chapter the artwork(thesis project) will be explained in detail. Final work and it's progress will be explained.

@@

%%
%%
\subsection{(Overcomed) Problems}
There are a lot of questions and problems that I have to overcome while development of my work. 
\begin{itemize}
\item First one is that my art work can be considered as design and has functional purposes. (It is not just a design, it is uses design to reach its goal like many artworks use other disciplines to reach their goals and expression. Purpose is not design and functionality.)
\item Using unused industrial paper. (Mixed trash and virgin material, \textbf{to show that discarded and desired object can live together.})
\item Collecting them with help of people, and asking other people to give the unused papers. (Collected from my close friends, from supervisor, from office where I work, from modshifters and varuna gezgin and from bcc labs(hopefully)?)
\item Giving them to people, but people should take them voluntarily.
\end{itemize}

@@

\subsection{What do I think about trash?}
I need to clarify my approach to the trash, wasting and discarding. First point is that I am very uncomfortable to the action of discarding thing. I always think that by discarding this think I am missing something rather than getting rid of something. Sometimes because of the significant amount of residue from consumption from daily activities I became overwhelmed and to move on I need to leave behind them and move on. However almost it is never ending loop. (I believe that sometimes we need to break the loops to realize different meanings. To think outside the box, we need to behave outside of common habits. As I mentioned the discarding things are some of the loops that we are rare to behave like other way.) \textbf{What am I discarding?} To get rid of my load and move on. But for what? and also ought to be like that? (throw away them to same bin. (Some of people do not care too much bin and throw them whenever it is possible.)) Even if I discard some stuff I think that I am ignoring its potential and losing it. At that times I become very sad and feel very comfortable. I must have find to another place for it more suitable than a waste bin. At least I can give them someone else who can use it for own purposes. Do I really luxury of discard?

Significance of thinking outside the box (about actually trash) is actually breaking the loops. You have to look at differently from your common perception. \textbf{Break the rules, break the loops.}

\textbf{Making exploration.} One of the encouraging factor is to work on trash is to find (or explore) something different from someone else's discard. Because it is discarded and undiscovered. Wait us to be discarded. and possible (as picasso mentioned) discovered again and again.

\section{Parts of project (or final work)}
The project introduced in this thesis have different parts. Each of them are connected to have relation with and support the other. Different parts also enable us that different level of integration to the project.

\subsection{Notebooks}
Mixing materials is main method in the production process. I combine different papers and packages. I try to generate every possible combination. For some of them I establish the connection but for the others the connection is not obvious but it is not obligatory. Because trash is state where you can find meaning through the trash or material later.

All package papers are cleaned up. Because it is important that it needs to be safe to use. With mix of water and little bleach they are swabbed.

\subsubsection{Name of notebooks}
\begin{itemize}
\item Puzzle, because it is cut out from very big and long banner (which is carried at graduation ceremony at METU). Every piece was a part of bigger banner. 
\item 12.00 pm. Burger King pockets from office where I work. Because it is launch time. It is collected at the same time.
\item ... because 
\item 08.00 am/gevrek, breakfast time. 
\end{itemize}

\subsubsection{Collected materials}
There are different papers and objects are used to produce papers
\begin{itemize}
\item Burger King packages, from office at launch time
\item Starbucks packages, from supervisor, office and my friend. Especially my supervisor and friend collect them from their friends and their own uses. They save them for me and later I take them later. 
\item Modshifters papers, that are covered on table and at the end of the day they are cut out and throw away. I go this place many times and every time questioned what they are doing to the papers. One of my visit we stay there at a late time and catch the garson collecting the old papers and prepearing tables to the next customer or day. I ask him to give me and he kindly accepted. From this paper I covered [x] notebooks. All of them contains track of people who sit down there. I do not know them and I am not sure that the paper that they are sit down turned to such a thing. 
\item Varuna Gezgin
\item Graduation banner
\end{itemize}

\subsection{Website}
As I think that finding a place the discarded items is one of the main purposes of this project. As it finds a place peoples life again, it also finds another place in the digital space. ()

Mainly websites displays the story(History) of notebooks. Also it is a place to track the journey the notebooks. As I claimed that it is not a finished work. It does not completed transformation. It always continues. Therefore a website that anyone can reach share their progress via website. Anyone can later discover how they turned to new things etc.

Collect peoples comment with this notebooks. As I leave notebooks different places I do not have connection with people who take them. This website also will help to collect/share peoples ideas about the notebooks.

It will contains a section for how notebooks are produced and the story behind it. The purpose is to record the creative process and share with the others. Revealing the process is significant to demystifiying the truth about the project. It makes it more clear that the object used here is actually transformed from something else.

\textbf{Why website?} Maybe you can think that there are different methods to accomplish recording and sharing the process. In a gallery on a single table or a room it can be succeed. However it like the idea that website can evolve by time as this work evolve in time. I think it matches perfectly. This is not a finished work, it continues and so the website also.

% Meaning of stories behind the process
There are different stories behind the objects. I try to record their stories (by photography and taking notes) but some of them were not possible. However I still use them in the work because even if I missed their story, with their materiality reveals their history. It still has a history but needs to rewritten. Maybe forgetting all the history maybe creates different notebook.

It is also co-authored work. Because many people helped me to collect the papers and also many people leave their trail to the paper and also they bring meaning to the them. After production of papers I also want them to continue as co-authored process. In other words many people will be part of this project. As people see different things on objects and bring them to me. the variety of things is increased in time. Because people sad me that \quotes{I thought that you can use it. Do you collect also these?}. After that time I want to continue as so.

% Documenting the progress.

% It was not only that such characteristic was clearly suited for the exploration of human spaces such as home, but it was also that I am comfortably and confidently fluent in practicing photography
